DRAFT: Scalable, Robust Multipath Communication on the Butterfly Network

### 2021-09-14 AttackTolerance/plosone/r1/NetFT-plosone-r1.tex

\begin{figure}[!h]
\centerline{\includegraphics{fig-perror}}
\caption{
The probability of an undetectable error as a function of the number of
redundant channels and the number of adversarial faults.
A small increase in the number of utilized paths (network traffic)
can compensate for a large increase in attacker power.
}
\label{fig:pfail}
\end{figure}

@@

\begin{figure}
\centerline{\includegraphics[width=4in,height=2.78in]{fig-partial-trust.pdf}}
\caption{
Illustration of a trusted communication network and the network properties
used by the {\em bounded trust model}.
Edges represent mutually trusted communication links.
The sender (Alice, $s$) and receiver (Bob, $t$) trust all nodes
less than the {\em trust radius} $h$ hops away.
These nodes form their {\em trusted neighborhoods} $T_h(v)$ and $T_h(w)$.
We assume that all faults occur in the remaining nodes: the
{\em untrusted region}.
The untrusted nodes in contact with the trusted neighborhoods for the
{\em trust boundaries} $B_h(v)$ and $B_h(w)$,
which (in the absence of central bottlenecks) determine the
{\em effective redundancy} $\delta_h$ provided by the network.
Alice and Bob can achieve the same level of attack-tolerance
as if they were directly connected by $\delta_h$ redundant channels.
}
\label{fig:trust-source}
\end{figure}

@@

\begin{figure}[!h]
\begin{center}
\includegraphics[height=3in]{fig-bf-route}
\end{center}
\caption{
A 3-dimensional wraparound butterfly network.
Note that the rightmost nodes are the same nodes as the leftmost,
drawn twice for visual clarity.
The highlighted nodes and edges show the path from node (0,000)
to node (1,101).
\label{fig:bf-route}
}
\end{figure}

\begin{figure}[!h]
\begin{center}
\includegraphics{fig-butterfly}
\end{center}
\caption{
Schematic illustration of the two types of edges in a directed butterfly
network.
The node $(l,z)$ is shown as the bit string $z$ with a square around the
$l$th bit.
``Down'' edges increment $l$, leaving $z$ unchanged,
while ``down-right'' edges increment $l$ and invert the $l$th bit of $z$.
In the wrap-around variant, the nodes with maximum $l$ have down and down-right
edges to the nodes with $l=0$.
\label{fig:butterfly}
}
\end{figure}

@@

\begin{figure}
\centerline{\includegraphics{fig-diameter}}
\caption{
Simulation of targeted attacks against a snapshot of the internet's router
network with a fraction of the edges rewired into a partial butterfly configuration.
The original network fragments when the top 1\% of nodes are removed.
With only 10\% of the butterfly edges present,
this value doubles to 2\%.
With 90\% of the edges rewired,
the network remains unfragmented beyond the failure of the 8\% most
central nodes.
The rewiring scheme does not require adding any additional edges.
}
\label{fig:diameter}
\end{figure}

\begin{figure*}[h!]
\centerline{\includegraphics[width=5in,height=5in]{fig-mincut}}
\caption{
Simulation of targeted attacks against a snapshot of the internet's router
network with a fraction of the edges rewired into a partial butterfly configuration.
The effective redundancy is shown for several values of trust transitivity $h$.
For $h>0$, the original network has higher effective redundancy up to a crossover point,
after which the rewired network performs better.
}
\label{fig:mincut}
\end{figure*}

@@

\begin{figure}[h!]
\begin{center}
\begin{tikzpicture}[
node distance=0pt,
 start chain = A going right,
    X/.style = {rectangle, draw,% styles of nodes in string (chain)
                minimum width=10ex, minimum height=3ex,
                outer sep=0pt, on chain},
                        ]
\foreach \i in {0\ldots,{\ldots}0\ldots,{\ldots}0\ldots,{\ldots}0}% <-- content of nodes
    \node[X] {\i};
\draw[<->] ([yshift=1.5mm] A-1.north east) -- node[above=0.25mm] {$h$} ([yshift=1.5mm] A-1.north west);
\draw[<->] ([yshift=1.5mm] A-2.north east) -- node[above=0.25mm] {$l_w - 2h$} ([yshift=1.5mm] A-2.north west);
\draw[<->] ([yshift=1.5mm] A-3.north east) -- node[above=0.25mm] {$h$} ([yshift=1.5mm] A-3.north west);
\draw[<->] ([yshift=1.5mm] A-4.north east) -- node[above=0.25mm] {$m - l_w$} ([yshift=1.5mm] A-4.north west);
\draw ( A-1.west) -- node[left=5ex,minimum width=10ex] {\underline{Stage}} ( A-1.west);
\end{tikzpicture}
\\
\begin{tikzpicture}[
node distance=0pt,
 start chain = A going right,
    X/.style = {rectangle, draw,% styles of nodes in string (chain)
                minimum width=10ex, minimum height=3ex,
                outer sep=0pt, on chain},
    Y/.style = {rectangle, draw,% styles of nodes in string (chain)
                minimum width=10ex, minimum height=3ex,
                outer sep=0pt, on chain, thick, fill=blue!20!white},
                        ]
\node[Y] {$s$};
\foreach \i in {{\ldots}0\ldots,{\ldots}0\ldots,{\ldots}0}% <-- content of nodes
    \node[X] {\i};
\draw ( A-1.west) -- node[left=5ex,minimum width=10ex] {1.} ( A-1.west);
\end{tikzpicture}
\\
\begin{tikzpicture}[
node distance=0pt,
 start chain = A going right,
    X/.style = {rectangle, draw,% styles of nodes in string (chain)
                minimum width=10ex, minimum height=3ex,
                outer sep=0pt, on chain},
    Y/.style = {rectangle, draw,% styles of nodes in string (chain)
                minimum width=10ex, minimum height=3ex,
                outer sep=0pt, on chain, thick, fill=blue!20!white},
                        ]
\foreach \i in {$s$}% <-- content of nodes
    \node[X] {\i};
\node[Y] {{\ldots}1\ldots};
\foreach \i in {{\ldots}0\ldots,{\ldots}0}% <-- content of nodes
    \node[X] {\i};
\draw ( A-1.west) -- node[left=5ex,minimum width=10ex] {2.} ( A-1.west);
\end{tikzpicture}
\\
\begin{tikzpicture}[
node distance=0pt,
 start chain = A going right,
    X/.style = {rectangle, draw,% styles of nodes in string (chain)
                minimum width=10ex, minimum height=3ex,
                outer sep=0pt, on chain},
    Y/.style = {rectangle, draw,% styles of nodes in string (chain)
                minimum width=10ex, minimum height=3ex,
                outer sep=0pt, on chain, thick, fill=blue!20!white},
                        ]
\foreach \i in {$s$,{\ldots}1\ldots}% <-- content of nodes
    \node[X] {\i};
\node[Y] {$\tilde{s}$};
\foreach \i in {{\ldots}0}% <-- content of nodes
    \node[X] {\i};
\draw ( A-1.west) -- node[left=5ex,minimum width=10ex] {3.} ( A-1.west);
\end{tikzpicture}
\\
\begin{tikzpicture}[
node distance=0pt,
 start chain = A going right,
    X/.style = {anchor=base, rectangle, draw,% styles of nodes in string (chain)
                minimum width=10ex, minimum height=3ex,
                outer sep=0pt, on chain},
    Y/.style = {rectangle, draw,% styles of nodes in string (chain)
                minimum width=10ex, minimum height=3ex,
                outer sep=0pt, on chain, thick, fill=blue!20!white},
                        ]
\foreach \i in {$s$,{\ldots}1\ldots,$\tilde{s}$}% <-- content of nodes
    \node[X] {\i};
\node[Y] {$z_{w,D}$};
\draw ( A-1.west) -- node[left=5ex,minimum width=10ex] {4.} ( A-1.west);
\end{tikzpicture}
\\
\begin{tikzpicture}[
node distance=0pt,
 start chain = A going right,
    X/.style = {anchor=base, rectangle, draw,% styles of nodes in string (chain)
                minimum width=10ex, minimum height=3ex,
                outer sep=0pt, on chain},
    Y/.style = {rectangle, draw,% styles of nodes in string (chain)
                minimum width=10ex, minimum height=3ex,
                outer sep=0pt, on chain, thick, fill=blue!20!white},
                        ]
\node[Y] {$z_{w,A}$};
\foreach \i in {{\ldots}1\ldots,$\tilde{s}$,$z_{w,D}$}% <-- content of nodes
    \node[X] {\i};
\draw ( A-1.west) -- node[left=5ex,minimum width=10ex] {5.} ( A-1.west);
\end{tikzpicture}
\\
\begin{tikzpicture}[
node distance=0pt,
 start chain = A going right,
    X/.style = {anchor=base, rectangle, draw,% styles of nodes in string (chain)
                minimum width=10ex, minimum height=3ex,
                outer sep=0pt, on chain},
    Y/.style = {rectangle, draw,% styles of nodes in string (chain)
                minimum width=10ex, minimum height=3ex,
                outer sep=0pt, on chain, thick, fill=blue!20!white},
                        ]
\foreach \i in {$z_{w,A}$}% <-- content of nodes
    \node[X] {\i};
\node[Y] {$z_{w,B}$};
\foreach \i in {$\tilde{s}$,$z_{w,D}$}% <-- content of nodes
    \node[X] {\i};
\draw ( A-1.west) -- node[left=5ex,minimum width=10ex] {6.} ( A-1.west);
\end{tikzpicture}
\\
\begin{tikzpicture}[
node distance=0pt,
 start chain = A going right,
    X/.style = {anchor=base, rectangle, draw,% styles of nodes in string (chain)
                minimum width=10ex, minimum height=3ex,
                outer sep=0pt, on chain},
    Y/.style = {rectangle, draw,% styles of nodes in string (chain)
                minimum width=10ex, minimum height=3ex,
                outer sep=0pt, on chain, thick, fill=blue!20!white},
                        ]
\foreach \i in {$z_{w,A}$,$z_{w,B}$}% <-- content of nodes
    \node[X] {\i};
\node[Y] {$z_{w,C}$};
\foreach \i in {$z_{w,D}$}% <-- content of nodes
    \node[X] {\i};
\draw ( A-1.west) -- node[left=5ex,minimum width=10ex] {7.} ( A-1.west);
\end{tikzpicture}
\end{center}
\caption{
Progression of place-within-level $z$ as the multipath routing algorithm
cycles through the levels of the butterfly network.
\label{fig:route-overview}
}
\end{figure}

\begin{figure}[!h]
\begin{center}
\includegraphics{fig-routing}
\end{center}
\caption{
An example of one path as constructed by the proposed multipath
routing algorithm.
The path is shown for $s = 10_2$
and $w = (6, 0110111_2)$.
\label{fig:routing}
}
\end{figure}

>>>>

\begin{figure}[!h]
%\centerline{\includegraphics{fig-perror}}
\caption{
The probability of an undetectable error as a function of the number of
redundant channels and the number of adversarial faults.
A small increase in the number of utilized paths (network traffic)
can compensate for a large increase in attacker power.
}
\label{fig:pfail}
\end{figure}

@@

\begin{figure}
%\centerline{\includegraphics[width=4in,height=2.78in]{fig-partial-trust.pdf}}
\caption{
Illustration of a trusted communication network and the network properties
used by the {\em bounded trust model}.
Edges represent mutually trusted communication links.
The sender (Alice, $s$) and receiver (Bob, $t$) trust all nodes
less than the {\em trust radius} $h$ hops away.
These nodes form their {\em trusted neighborhoods} $T_h(v)$ and $T_h(w)$.
We assume that all faults occur in the remaining nodes: the
{\em untrusted region}.
The untrusted nodes in contact with the trusted neighborhoods for the
{\em trust boundaries} $B_h(v)$ and $B_h(w)$,
which (in the absence of central bottlenecks) determine the
{\em effective redundancy} $\delta_h$ provided by the network.
Alice and Bob can achieve the same level of attack-tolerance
as if they were directly connected by $\delta_h$ redundant channels.
}
\label{fig:trust-source}
\end{figure}

@@

\begin{figure}[!h]
\begin{center}
%\includegraphics[height=3in]{fig-bf-route}
\end{center}
\caption{
A 3-dimensional wraparound butterfly network.
Note that the rightmost nodes are the same nodes as the leftmost,
drawn twice for visual clarity.
The highlighted nodes and edges show the path from node (0,000)
to node (1,101).
\label{fig:bf-route}
}
\end{figure}

\begin{figure}[!h]
\begin{center}
%\includegraphics{fig-butterfly}
\end{center}
\caption{
Schematic illustration of the two types of edges in a directed butterfly
network.
The node $(l,z)$ is shown as the bit string $z$ with a square around the
$l$th bit.
``Down'' edges increment $l$, leaving $z$ unchanged,
while ``down-right'' edges increment $l$ and invert the $l$th bit of $z$.
In the wrap-around variant, the nodes with maximum $l$ have down and down-right
edges to the nodes with $l=0$.
\label{fig:butterfly}
}
\end{figure}

@@

\begin{figure}
%\centerline{\includegraphics{fig-diameter}}
\caption{
Simulation of targeted attacks against a snapshot of the internet's router
network with a fraction of the edges rewired into a partial butterfly configuration.
The original network fragments when the top 1\% of nodes are removed.
With only 10\% of the butterfly edges present,
this value doubles to 2\%.
With 90\% of the edges rewired,
the network remains unfragmented beyond the failure of the 8\% most
central nodes.
The rewiring scheme does not require adding any additional edges.
}
\label{fig:diameter}
\end{figure}

\begin{figure*}[h!]
%\centerline{\includegraphics[width=5in,height=5in]{fig-mincut}}
\caption{
Simulation of targeted attacks against a snapshot of the internet's router
network with a fraction of the edges rewired into a partial butterfly configuration.
The effective redundancy is shown for several values of trust transitivity $h$.
For $h>0$, the original network has higher effective redundancy up to a crossover point,
after which the rewired network performs better.
}
\label{fig:mincut}
\end{figure*}

@@

\begin{figure}[h!]
\caption{
Progression of place-within-level $z$ as the multipath routing algorithm
cycles through the levels of the butterfly network.
\label{fig:route-overview}
}
\end{figure}

\begin{figure}[!h]
\begin{center}
%\includegraphics{fig-routing}
\end{center}
\caption{
An example of one path as constructed by the proposed multipath
routing algorithm.
The path is shown for $s = 10_2$
and $w = (6, 0110111_2)$.
\label{fig:routing}
}
\end{figure}

### 2021-09-14 AttackTolerance/plosone/r4/Manuscript.tex

\end{flushleft}
% Please keep the abstract below 300 words
\section*{Abstract}
It is crucial for large-scale communication networks such as the internet
to be resilient against attacks\cite{sterbenz_resilience_2010}
such as censorship and surveillance,
which pose a threat to free expression and free association.
Self-organized networks such as the internet’s router network typically have
heavy-tailed degree distributions\cite{barabasi_scale-free_2009},
making them highly vulnerable to targeted attacks against central nodes
\cite{albert_error_2000}.
While cryptographic solutions exist,
they fail to address the underlying topological problem,
and remain vulnerable to
man-in-the-middle attacks \cite{nayak_different_2010}
and coercion \cite{grewal_caveat_2013}.
Coercion-resistant, topological approaches to attack tolerance are needed to
address the current vulnerability of communications infrastructure to
censorship and surveillance.
We present a novel concurrent multipath routing (CMR) algorithm for the
wraparound butterfly network topology,
as well as a highly attack-tolerant Structured Multipath Fault Tolerance (SMFT)
architecture which incorporates the butterfly CMR algorithm. We also identify a
previously unexplored relationship between network topology, trust transitivity,
and attack-tolerance, and provide a framework for further exploration of this
relationship. Our work is the first theoretical demonstration of a point-to-point
communication network architecture that can resist coercion and other
non-technical attacks, without requiring infinitely transitive trust.
To address cases where the network structure cannot be fully controlled,
we demonstrate how a snapshot of the internet’s router network can be partially
rewired for greater attack-tolerance.
More broadly, we hope that this work will serve as a starting point for the
evelopment of additional topology-based attack-tolerant communication
architectures to guard against the dangers of censorship and surveillance.

>>>>

\end{flushleft}
% Please keep the abstract below 300 words
\section*{Abstract}
It is crucial for large-scale communication networks such as the internet
to be resilient against attacks
such as censorship and surveillance,
which pose a threat to free expression and free association.
Self-organized networks such as the internet’s router network typically have
heavy-tailed degree distributions,
making them highly vulnerable to targeted attacks against central nodes.
While cryptographic solutions exist,
they fail to address the underlying topological problem,
and remain vulnerable to
man-in-the-middle attacks
and coercion.
Coercion-resistant, topological approaches to attack tolerance are needed to
address the current vulnerability of communications infrastructure to
censorship and surveillance.
We present a novel concurrent multipath routing (CMR) algorithm for the
wraparound butterfly network topology,
as well as a highly attack-tolerant Structured Multipath Fault Tolerance (SMFT)
architecture which incorporates the butterfly CMR algorithm. We also identify a
previously unexplored relationship between network topology, trust transitivity,
and attack-tolerance, and provide a framework for further exploration of this
relationship. Our work is the first theoretical demonstration of a point-to-point
communication network architecture that can resist coercion and other
non-technical attacks, without requiring infinitely transitive trust.
To address cases where the network structure cannot be fully controlled,
we demonstrate how a snapshot of the internet’s router network can be partially
rewired for greater attack-tolerance.
More broadly, we hope that this work will serve as a starting point for the
evelopment of additional topology-based attack-tolerant communication
architectures to guard against the dangers of censorship and surveillance.
